\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-29 OaklandSubmission/security.tex
minor

We shall assume a cryptographic \mpc backend that securely implements any circuit $\crct$ that is output by our compiler (see \figureref{circuits}). In more detail, this means that for any well-typed source program $s$, let $\crct$ be the circuit output by our compiler (as in \theoremref{correctness}). We assume that there exists a \mpc protocol $\prot$ that securely realizes the functionality $\crct$ and let $\simu_{\tiny{2pc}}$ be the corresponding simulator  (that runs on $\crct$, input of the corrupt party and the output obtained from trusted functionality for $\crct$). We note that the work of \cite{aby} provides such a protocol $\prot$ and simulator $\simu_{\tiny{2pc}}$ for all circuits $\crct$ output by our compiler\footnote{\divya{We note that \cite{aby} provides a \mpc protocol for a more general .....}}. We are now ready to state and prove our security theorem.

>>>>

We shall assume a cryptographic \mpc backend that securely implements any circuit $\crct$ that is output by our compiler (see \figureref{circuits}). In more detail, this means that for any well-typed source program $s$, let $\crct$ be the circuit output by our compiler (as in \theoremref{correctness}). We assume that there exists a \mpc protocol $\prot$ that securely realizes the functionality $\crct$ and let $\simu_{\tiny{2pc}}$ be the corresponding simulator  (that runs on $\crct$, input of the corrupt party and the output obtained from trusted functionality for $\crct$). We note that the work of \cite{aby} provides such a protocol $\prot$ and simulator $\simu_{\tiny{2pc}}$ for all circuits $\crct$ output by our compiler. We are now ready to state and prove our security theorem.
